---
title: "My Reading History"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: html_document
---

<style>
.leaflet {
   margin: auto;
   margin-top: 30px;
   margin-bottom: 30px;
}

.figure {
   margin-top: 100px;
   margin-bottom: 100px;
}

table {
    margin-top: 100px;
    margin-bottom: 100px !important;
}

.container { width: 800px; }

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(leaflet)
library(ggplot2)
library(treemap)

source("processData.R")

```


## Reading the World

<div style="margin-bottom:30px;">

In the build up to the 2018 World Cup.  

Even finding and obtaining a book (translated to English) to read for some countries proved to be a tricky task.  


```{r echo= FALSE}

pal.all <- colorFactor(palette = c("#8d96a3", "#fdbb84", "#e34a33"),
                        domain = world.dat.new@data$all.bin)
                   
labels.all <- sprintf(
  "<strong>%s</strong><br/>Books Owned - %g <br />Books Read - %g",
  world.dat.new@data$ADMIN, world.dat.new@data$own.count, world.dat.new@data$read.count
) %>% lapply(htmltools::HTML)

world.dat.new %>% 
  leaflet(width = "100%") %>% 
  addPolygons(fillColor = ~pal.all(all.bin),
              weight = 0.5,
              opacity = 1,
              color = "black",
              fillOpacity = 0.7,
              highlightOptions = highlightOptions(color = "white", weight = 2, bringToFront = TRUE),
              label = labels.all,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "15px",
                direction = "auto")) %>%
  addLegend(pal = pal.all, values = ~all.bin, opacity = 0.7, title = "Read Status",
            position = "bottomright")



``` 

</div>

<div style="margin-bottom:30px;">

Since making a concious effort in 2018 to try to read more widely I have definitely managed to broaden my reading horizons, but my reading history is still dominated by authors from primarily English speaking countries. 

</div>


```{r echo= FALSE, fig.align = "center", fig.margin = TRUE, width = 800, warning=FALSE}
treemap(country.summary,
        # data
        index="ADMIN",
        vSize="read.count",
        type="index",
        
        # Main
        title="",
        palette="Dark2",
        
        # Borders:
        border.col=c("black"),             
        border.lwds=1,                         
        
        # Labels
        fontsize.labels=0.5,
        fontcolor.labels="white",
        fontface.labels=1,            
        bg.labels=c("transparent"),              
        align.labels=c("center", "center"),                                  
        overlap.labels=0.5,
        inflate.labels=T                        # If true, labels are bigger when rectangle is bigger.
        )

``` 

